Natural variation in teosinte at the domestication locus teosinte branched1 (tb1)

### 2014-04-21 manuscript.tex
edits

Genotype of the Hopscotch insertion was confirmed with two PCRs for 837 individuals. Among the 247 maize landrace accessions genotyped, all but 8 were homozygous for the presence of the insertion (\ref{TableS1Mays}, \ref{TableS2}). \jri{please fix table/figure references to say table/figure} Within our \emph{parviglumis} and \emph{mexicana} samples we found the Hopscotch insertion segregating in 37 and 4 populations \jri{this is confusing as the map shows <37 populations. we should be consistent about reporting for all pops, or all pops with n>8, etc. or at least be explicit what cutoff we are using for each result}, respectively, and at highest frequency in the states of Jalisco, Colima, and Michoac\'{a}n in central-western Mexico in both subspecies (\ref{Fig1Map}) \jri{the map only shows parviglumis. can we add mexicana? the text makes it seem as if both should be on the map}. We examined Hardy-Weinberg equilibrium in a total of 14 populations (10 \emph{parviglumis} and 4 \emph{mexicana}) with more than 8 individuals sampled per population. Three populations (RIMPA0073, RIMPA0093, and RIMPA0158) show evidence of deviations from expected genotype frequencies under the assumptions of HWE (p<0.05).  \jri{in what direction? too many hets? what's the F? }

@@

Using our Hopscotch genotyping data, we calculated differentiation between populations (F\textsubscript{ST}) and subspecies (F\textsubscript{CT}) for populations in which we sampled 8 or more alleles. F\textsubscript{CT} is 0 within our dataset, and we found similar levels of F\textsubscript{ST} among populations within each subspecies (0.22) \jri{is this an average? this comes from libsequence?} and among all populations (0.23), to those reported in genome-wide estimates from previous studies \cite{Pyhajarvi2013} (\ref{Table1Fst}). \jri{the table caption says just sequence data, but it has hopscotch genotypes too}
% Table 1
\begin{table}[htbp]
  \centering
  \caption{Pairwise F\textsubscript{CT} values from sequence data}
    \begin{tabular}{lccc}
 %   \toprule
    \multicolumn{1}{c}{\textbf{Comparison}} & \textbf{Seq. Region 2} & \textbf{Seq.  Region 1} & \textbf{Hopscotch} \\
 %   \midrule
    EjuA \& EJuB & 0     & 0     & 0 \\
    EjuA \& MSA & 0.328 & 0.326 & 0.186 \\
    EjuA \& SLO & 0.258 & 0.416 & 0.28 \\
    EjuB \& MSA & 0.365 & 0.397 & 0.188 \\
    EjuB \& SLO & 0.29  & 0.512 & 0.28 \\
    MSA \& SLO & 0     & 0.007 & 0.016 \\
%    \bottomrule
    \end{tabular}
  \label{Table1Fst}
\end{table}
Although we found large variation in Hopscotch allele frequency among our populations, BayEnv analysis did not indicate a correlation between the Hopscotch insertion and environmental variables (all Bayes Factors $<$ 1; \ref{TableS3BayEnv}).

>>>>

Genotype of the Hopscotch insertion was confirmed with two PCRs for 837 individuals. Among the 247 maize landrace accessions genotyped, all but 8 were homozygous for the presence of the insertion (\ref{TableS1Mays}, \ref{TableS2}). \jri{please fix table/figure references to say table/figure} Within our \emph{parviglumis} and \emph{mexicana} samples we found the Hopscotch insertion segregating in 37 and 4 populations \jri{this is confusing as the map shows <37 populations. we should be consistent about reporting for all pops, or all pops with n>8, etc. or at least be explicit what cutoff we are using for each result}, respectively, and at highest frequency in the states of Jalisco, Colima, and Michoac\'{a}n in central-western Mexico in both subspecies (\ref{Fig1Map}) \jri{the map only shows parviglumis. can we add mexicana? the text makes it seem as if both should be on the map}. We examined Hardy-Weinberg equilibrium in a total of 14 populations (10 \emph{parviglumis} and 4 \emph{mexicana}) with more than 8 individuals sampled per population. Three populations (RIMPA0073, RIMPA0093, and RIMPA0158) show evidence of deviations from expected genotype frequencies under the assumptions of HWE (p<0.05).  \jri{in what direction? too many hets? what's the F? } \lev{they weren't all in the same direction, do you still want me to list out?}

@@

Using our Hopscotch genotyping data, we calculated differentiation between populations (F\textsubscript{ST}) and subspecies (F\textsubscript{CT}) for populations in which we sampled 8 or more alleles. F\textsubscript{CT} is 0 within our dataset, and we found similar levels of F\textsubscript{ST} among populations within each subspecies (0.22) \jri{is this an average? this comes from libsequence?} and among all populations (0.23), to those reported in genome-wide estimates from previous studies \cite{Pyhajarvi2013} (\ref{Table1Fst}).

% Table 1
\begin{table}[htbp]
  \centering
  \caption{Pairwise F\textsubscript{CT} values from sequence and Hopscotch genotyping data}
    \begin{tabular}{lccc}
 %   \toprule
    \multicolumn{1}{c}{\textbf{Comparison}} & \textbf{Seq. Region 2} & \textbf{Seq.  Region 1} & \textbf{Hopscotch} \\
 %   \midrule
    EjuA \& EJuB & 0     & 0     & 0 \\
    EjuA \& MSA & 0.328 & 0.326 & 0.186 \\
    EjuA \& SLO & 0.258 & 0.416 & 0.28 \\
    EjuB \& MSA & 0.365 & 0.397 & 0.188 \\
    EjuB \& SLO & 0.29  & 0.512 & 0.28 \\
    MSA \& SLO & 0     & 0.007 & 0.016 \\
%    \bottomrule
    \end{tabular}
  \label{Table1Fst}
\end{table}
Although we found large variation in Hopscotch allele frequency among our populations, BayEnv analysis did not indicate a correlation between the Hopscotch insertion and environmental variables (all Bayes Factors $<$ 1; \ref{TableS3BayEnv}).
